DATA 624 Homework 5

### 2020-03-06 DATA624/HW5.Rmd
More work on HW5

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(fpp2)
options(scipen=999)
```

@@

**The RMSE for the paperback model is 33.6 and 31.9 for the hardback model.**

@@

@@

@@

@@

@@

@@

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(fpp2)
library(kableExtra)
library(gridExtra)
library(readxl)
options(scipen=999)
```

@@

**The RMSE for the paperback model is `r round(accuracy(ses_paperback)[2], 2)` and `r round(accuracy(ses_hardback)[2], 2)` for the hardback model.**

@@

```{r}
holt_paperback <- holt(books[, 1], h = 4)
summary(holt_paperback)
```

```{r}
holt_hardback <- holt(books[, 2], h = 4)
autoplot(holt_hardback) +
  ylab("Hardback Book Sales")
summary(holt_hardback)
```

@@

**Holt's method does a better job than the SES models, because the RMSE is smaller for both the paperback and hardback series.  This is understandable because Holt's includes a trend component.  SES assumes there is no trend.  This does not really fit these timeseries.**

```{r, echo=FALSE}
data.frame(Type = c('Paperback', 'Hardback'),
           SES = c(accuracy(ses_paperback)[2], accuracy(ses_hardback)[2]),
           Holt = c(accuracy(holt_paperback)[2], accuracy(holt_hardback)[2])
           ) %>%
  rename(`Holt's Method` = Holt) %>%
  kable() %>%
  kable_styling()
```

@@

```{r}
p1 <- autoplot(ses_paperback) + ylab("Paperback Book Sales") + ggtitle("SES Forecast")
p2 <- autoplot(holt_paperback) + ylab("Paperback Book Sales") + ggtitle("Holt's Forecast")
grid.arrange(p1, p2, ncol = 2)
```

```{r}
p1 <- autoplot(ses_hardback) + ylab("Hardback Book Sales") + ggtitle("SES Forecast")
p2 <- autoplot(holt_hardback) + ylab("Hardback Book Sales") + ggtitle("Holt's Forecast")
grid.arrange(p1, p2, ncol = 2)
```

**I think Holt's method is a better forecast.  I like that factors in the trend.**

@@

```{r}
cat("Paperback:", holt_paperback$mean[1] - 1.96 * accuracy(holt_paperback)[2], "to", holt_paperback$mean[1] + 1.96 * accuracy(holt_paperback)[2])
```
```{r}
cat("Hardback:", holt_hardback$mean[1] - 1.96 * accuracy(holt_hardback)[2], "to", holt_hardback$mean[1] + 1.96 * accuracy(holt_hardback)[2])
```

**The 95% CI for the paperback series generated by Holt's method is 143.9130  to 275.0205.  This is wider than the CI computed above.  The CI for hardbacks from Holt's method is 192.9222 to 307.4256, which again is wider than the CI above.**

@@

```{r}
h <- 100

holt_eggs <- holt(eggs, h=h)
box_cox_eggs <- holt(eggs, h=h, lambda=TRUE)
damped_eggs <- holt(eggs, h=h, damped=TRUE)
damped_box_cox_eggs <- holt(eggs, h=h, damped=TRUE, lambda=TRUE)
exponential_eggs <- holt(eggs, h=h, exponential=TRUE)

autoplot(holt_eggs) + ggtitle("Holt's Method") 
autoplot(damped_eggs) + ggtitle("Damped")
autoplot(box_cox_eggs) + ggtitle("Box-Cox")
autoplot(damped_box_cox_eggs) + ggtitle("Damped & Box-Cox")
autoplot(exponential_eggs) + ggtitle("Exponential")
```

```{r}
get_rmse <- function(model){
  accuracy(model)[2]
}

Model <- c("Holt's Linear", 
           "Box-Cox Transformed",
           "Damped",
           "Damped and Box-Cox",
           "Exponential")

RMSE <- c(get_rmse(holt_eggs), 
          get_rmse(box_cox_eggs),
          get_rmse(damped_eggs),
          get_rmse(damped_box_cox_eggs),
          get_rmse(exponential_eggs))

eggs_rmse_df <- data.frame(Model, RMSE)

eggs_rmse_df %>%
  kable() %>%
  kable_styling()
```

**The model with the lowest (best) RMSE is the `r eggs_rmse_df[eggs_rmse_df$RMSE == min(eggs_rmse_df$RMSE),]$Model` model.**

@@

```{r}
retaildata <- read_excel("retail.xlsx", skip = 1)
retail_ts <- ts(retaildata[, "A3349873A"], frequency = 12, start = c(1982, 4))

hw_multiplicative <- hw(retail_ts, seasonal = "multiplicative")
autoplot(hw_multiplicative) + 
  ggtitle("Multiplicative") + 
  ylab("Retail Sales")

hw_multiplicative_damped <- hw(retail_ts, seasonal = "multiplicative", damped = TRUE)
autoplot(hw_multiplicative_damped) + 
  ggtitle("Multiplicative & Damped") + 
  ylab("Retail Sales")
```
